---
title: "Cost effective analysis of second line therapy in RRMM in India"
author: "Dr Suman Kumar"
date: "16 January 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mother Study

[Parent article](http://dx.doi.org/10.1016/j.clinthera2017.08.010)

## Inclusion criteria

Post multiple regimens (median 5)

## Arms

1.  [MM-002](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3962162/): 
POM-d

1.  [SIRIUS]( http://dx.doi.org/10.1016/S0140-6736&#40;15&#41;01120-4): Daratumumab

1.  [PX-171-003-A1](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4123387/): Carfilzomib

## Multistate model

1.  Progression Free state

1.  Post Progression state

1.  Death

- Time horizon of 3 years was considered for economic model.

- 28 days cycle was used for each regimen.

- All patients assumed to be in progression free state at the start.

- Subsequent cycles, either of the three states.

- Once in post progressive state, they will not return to progression 
free state

- **Transition probability to PP state treatment specific**

    - POM-d: gompertz distribution 
        - Scale -1.77, normal, se 0.015
        - Shape 0.03, normal, se 0.002

    - vs DARA: HR
        - 0.95 (LB 0.67, UB 1.33, log normal, se 0.045)
    
    - vs CAR: HR
        - 0.83 (LB 0.61, UB 1.12, log normal, se 0.038)

- **PF state -> Death:** per cycle fatal progression probability.

    - Same for all the three groups
    - 0.022 (LB 0.013, UB 0.036, beta, se 0.06)

- **Post progression survival (PPS):** Common PPS curve will be used

    - Gompertz curve
        - Scale: -2.94, norm, se 0.108
        - Shape: 0.02, norm, se 0.008

    - We will use rgompertz function to get the random smaples and 
    will not use the normal distribution of scale and shape 
    parameters as they are leading to absurd distribution
    
```{r}
pgompertz(seq(0, 0.15, 0.001), shape = 2.94, rate = 1/0.02)
```

- **Time to treatment failure:** defined as time from the initiation 
of treatment with study drug till disease progression, death or 
treatment discontinuation. **PP state**, has common TTF curve.

    - PFS
        - POM-d: HR 1.19, (LB 0.95, UB 1.43), log normal se 0.045
        - DARA: HR 1.13, (LB 0.9, UB 1.36), log normal se 0.045
        - CAR: HR 1.03, (LB 0.82, UB 1.24), log normal se 0.038

## Conduct of trial

1.  All patients start with PF state.

1.  Depending on the distribution, each patient can go in 
either PP or death.

1.  The treatment depends on the conditional probability.

1.  Once in PP state, he can only go in Death or continue 
in PP state.

1.  Each of the patient time line will be divided into 28 d
cycles.

1.  Each cycle (end) will have following values:
    a.  State: PF, PP, Death
    b.  Therapy: Any of the treatment protocols or no treatment
    c.  Adverse events
    
    
## Adverse Effects

### POM-d

Median follow up of 14.1 months among 113 patients:

Total patient months  = `r 14.1 * 113`

